A thermodynamic view of dusty protoplanetary disks

### 2017-07-12 paper.tex
added ref to hopkins 17

These instabilities can trigger turbulence, and (in different regimes) promote or inhibit  
planetesimal formation. 
More recently, new 
dusty instabilities have appeared in numerical  
simulations \citep{loren15,loren16,lamb16} and analytical calculations \citep{squire17},   
but their physical underpinnings are not yet well 
understood.

>>>>

These instabilities can trigger turbulence, and (in different regimes) promote or inhibit  
planetesimal formation. 
More recently, new 
dusty instabilities have appeared in numerical  
simulations \citep{loren15,loren16,lamb16} and analytical calculations \citep{squire17,hopkins17},   
but their physical underpinnings are not yet well 
understood.
